Simulating physiological flexibility in the acute glucocorticoid response to stressors reveals limitations of current empirical approaches

### 2022-06-30 3_r_scripts/Revision.Rmd
Editing text.

I developed a set of functions in R version 4.0.2 [@rcore] to generate acute physiological response curves. This simulation makes no assumptions about the  mechanistic process that results in the shape of a glucocorticoid response. Rather, parameters are sampled to generate curves that are similar in shape and degree of variation to empirically observed responses (Figure \@ref(fig:concept-fig)). This simulation is designed to create data sets with realistic structure that can be used to better design and plan studies of physiological flexibility, to evaluate power of current study designs, and to evaluate the sensitivity of sampling regimes to any number of modifications to the shape of glucocorticoid response curves (e.g., changing covariation patterns between different features of the response). I explore a small number of scenarios in the next section, but I expect that many other scenarios can be addressed with these tools. For illustration purposes, I refer to simulated glucocorticoid responses, but the simulation applies equally well to any physiological mediator of a rapid response. The code for the complete simulation along with full documentation of each function and argument can be accessed in a GitHub repository with a current version permanently archived on Zenodo (LINK). The package can be installed directly within the R environment using the following command.

@@

Each of the scenarios described here uses the basic simulation functions described above with input parameters adjusted to address the question of interest. A complete set of reproducible code to create all of the examples presented here is available on GitHub and permanenty archived at Zenodo (https://github.com/cct663/speed_vs_scope).

>>>>

I developed a set of functions in R version 4.0.2 [@rcore] to generate acute physiological response curves. This simulation makes no assumptions about the  mechanistic process that results in the shape of a glucocorticoid response. Rather, parameters are sampled to generate curves that are similar in shape and degree of variation to empirically observed responses (Figure \@ref(fig:concept-fig)). This simulation is designed to create data sets with realistic structure that can be used to better design and plan studies of physiological flexibility, to evaluate power of current study designs, and to evaluate the sensitivity of sampling regimes to any number of modifications to the shape of glucocorticoid response curves (e.g., changing covariation patterns between different features of the response). I explore a small number of scenarios in the next section, but I expect that many other scenarios can be addressed with these tools. For illustration purposes, I refer to simulated glucocorticoid responses, but the simulation applies equally well to any physiological mediator of a rapid response. The code for the complete simulation along with full documentation of each function and argument can be accessed in a GitHub repository with a current version permanently archived on Zenodo (https://doi.org/10.5281/zenodo.6784207). The package can be installed directly within the R environment using the following command.

@@

Each of the scenarios described here uses the basic simulation functions described above with input parameters adjusted to address the question of interest. A complete set of reproducible code to create all of the examples presented here is available on GitHub and permanenty archived at Zenodo (https://doi.org/10.5281/zenodo.6784203).
